---
title: "MapsOfClimateVariables"
author: "KM"
date: "2022-08-30"
output: html_document
---

This script creates maps for climatic variables in the wet season by month. The AOI is Hwange. Script needs raster files saved as .tifs and stored chronologically in folders. Wet season is months Oct, Nov, Dec, Jan, Feb and March (inclusive).

```{r setup, include=FALSE}
library(raster)
library(ggplot2)

knitr::opts_chunk$set(echo = TRUE)
```




```{r import files}
#first import all files in a single folder as a list 
rastlistLST <- list.files(path = "~/Desktop/WMA/MappingClimateVariables/MappingClimateVariables/LST", pattern='.tif$', all.files=TRUE, full.names=T)
StackLST<-stack(rastlistLST)

rastlistNDVI <- list.files(path = "~/Desktop/WMA/MappingClimateVariables/MappingClimateVariables/NDVI", pattern='.tif$', all.files=TRUE, full.names=T)
StackNDVI<-stack(rastlistNDVI)

rastlistPrecip <- list.files(path = "~/Desktop/WMA/MappingClimateVariables/MappingClimateVariables/Precip", pattern='.tif$', all.files=TRUE, full.names=T)
StackPrecip<-stack(rastlistPrecip)

rastlistSoil <- list.files(path = "~/Desktop/WMA/MappingClimateVariables/MappingClimateVariables/Soil", pattern='.tif$', all.files=TRUE, full.names=T)
StackSoil<-stack(rastlistSoil)

```


NDVI
```{r separate into wet seasons, echo = FALSE}

WetSsn1516<-subset(StackNDVI,10:15)

WetSsb1516Plot<-spplot(WetSsn1516, zcol = names(WetSsn1516), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2015-2016 wet season NDVI values by month")
WetSsb1516Plot

WetSsn1617<-subset(StackNDVI,22:27)

WetSsn1617Plot<-spplot(WetSsn1617, zcol = names(WetSsn1617), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2016-2017 wet season NDVI values by month")
WetSsn1617Plot

WetSsn1718<-subset(StackNDVI,34:39)

WetSsn1718Plot<-spplot(WetSsn1718, zcol = names(WetSsn1718), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2017-2018 wet season NDVI values by month")
WetSsn1718Plot

WetSsn18<-subset(StackNDVI,46:48)

WetSsn18Plot<-spplot(WetSsn18, zcol = names(WetSsn18), names.attr=c("10", "11", "12"),  main = "2018 wet season NDVI values by month")
WetSsn18Plot
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


Precipitation
```{r separate into wet seasons, echo = FALSE}

PrcpWetSsn1516<-subset(StackPrecip,10:15)

PrcpWetSsn1516Plot<-spplot(PrcpWetSsn1516, zcol = names(PrcpWetSsn1516), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2015-2016 wet season precipitation by month")
PrcpWetSsn1516Plot

PrcpWetSsn1617<-subset(StackPrecip,22:27)

PrcpWetSsn1617Plot<-spplot(PrcpWetSsn1617, zcol = names(PrcpWetSsn1617), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2016-2017 wet season precipitation by month")
PrcpWetSsn1617Plot

PrcpWetSsn1718<-subset(StackPrecip,34:39)

PrcpWetSsn1617Plot<-spplot(PrcpWetSsn1617, zcol = names(PrcpWetSsn1617), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2017-2018 wet season precipitation by month")
PrcpWetSsn1617Plot

PrcpWetSsn18<-subset(StackPrecip,46:48)

PrcpWetSsn18Plot<-spplot(PrcpWetSsn18, zcol = names(PrcpWetSsn18), names.attr=c("10", "11", "12"),  main = "2018 wet season precipitation by month")
PrcpWetSsn18Plot
```

Soil moisture

```{r separate into wet seasons, echo = FALSE}

SoilWetSsn1516<-subset(StackSoil,10:15)

SoilWetSsn1516Plot<-spplot(SoilWetSsn1516, zcol = names(SoilWetSsn1516), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2015-2016 wet season soil moisture by month")
SoilWetSsn1516Plot

SoilWetSsn1617<-subset(StackSoil,22:27)

SoilWetSsn1617Plot<-spplot(SoilWetSsn1617, zcol = names(SoilWetSsn1617), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2016-2017 wet season soil moisture by month")
SoilWetSsn1617Plot

SoilWetSsn1718<-subset(StackSoil,34:39)

SoilWetSsn1617Plot<-spplot(SoilWetSsn1617, zcol = names(SoilWetSsn1617), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2017-2018 wet season soil moisture by month")
SoilWetSsn1617Plot

SoilWetSsn18<-subset(StackSoil,46:48)

SoilWetSsn18Plot<-spplot(SoilWetSsn18, zcol = names(SoilWetSsn18), names.attr=c("10", "11", "12"),  main = "2018 wet season soil moisture by month")
SoilWetSsn18Plot
```
LST

```{r separate into wet seasons, echo = FALSE}

LSTWetSsn1516<-subset(StackLST,10:15)

LSTWetSsn1516Plot<-spplot(LSTWetSsn1516, zcol = names(LSTWetSsn1516), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2015-2016 wet season LST by month")
LSTWetSsn1516Plot

LSTWetSsn1617<-subset(StackLST,22:27)

LSTWetSsn1617Plot<-spplot(LSTWetSsn1617, zcol = names(LSTWetSsn1617), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2016-2017 wet season LST by month")
LSTWetSsn1617Plot

LSTWetSsn1718<-subset(StackLST,34:39)

LSTWetSsn1617Plot<-spplot(LSTWetSsn1617, zcol = names(LSTWetSsn1617), names.attr=c("10", "11", "12", "1", "2","3"),  main = "2017-2018 wet season LST by month")
LSTWetSsn1617Plot

LSTWetSsn18<-subset(StackLST,46:48)

LSTWetSsn18Plot<-spplot(LSTWetSsn18, zcol = names(LSTWetSsn18), names.attr=c("10", "11", "12"),  main = "2018 wet season LST by month")
LSTWetSsn18Plot
```
